Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2023-12-28 src/naomi-simple_ks/ks.Rmd
Called "Latent" not "Latent field" now
Update KS plots for thesis

## `beta_rho`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_list("beta_rho")
```

## `beta_alpha`

```{r eval = pars_eval[["beta_alpha"]]}
histogram_and_ecdf_list("beta_alpha")
```

## `beta_lambda`

```{r eval = pars_eval[["beta_lambda"]]}
histogram_and_ecdf_list("beta_lambda")
```

## `beta_anc_rho`

```{r eval = pars_eval[["beta_anc_rho"]]}
histogram_and_ecdf_list("beta_anc_rho")
```

## `beta_anc_alpha`

```{r eval = pars_eval[["beta_anc_alpha"]]}
histogram_and_ecdf("beta_anc_alpha")
```

## `logit`

```{r eval = FALSE}
lapply(pars[stringr::str_starts(pars, "logit")], histogram_and_ecdf)
```

## `log_sigma`

```{r eval = FALSE}
lapply(pars[stringr::str_starts(pars, "log_sigma")], histogram_and_ecdf)
```

## `u_rho_x`

```{r eval = pars_eval[["u_rho_x"]]}
histogram_and_ecdf_list("u_rho_x")
```

## `us_rho_x`

```{r eval = pars_eval[["us_rho_x"]]}
histogram_and_ecdf_list("us_rho_x")
```

## `u_rho_xs`

```{r eval = pars_eval[["u_rho_xs"]]}
histogram_and_ecdf_list("u_rho_xs")
```

## `us_rho_xs`

```{r eval = pars_eval[["us_rho_xs"]]}
histogram_and_ecdf_list("us_rho_xs")
```

## `u_rho_as`

```{r eval = pars_eval[["u_rho_as"]]}
histogram_and_ecdf_list("u_rho_as")
```

## `u_alpha_x`

```{r eval = pars_eval[["u_alpha_x"]]}
histogram_and_ecdf_list("u_alpha_x")
```

## `us_alpha_x`

```{r eval = pars_eval[["us_alpha_x"]]}
histogram_and_ecdf_list("us_alpha_x")
```

## `u_alpha_xs`

```{r eval = pars_eval[["u_alpha_xs"]]}
histogram_and_ecdf_list("u_alpha_xs")
```

## `us_alpha_xs`

```{r eval = pars_eval[["beta_rho"]]}
histogram_and_ecdf_list("us_alpha_xs")
```

## `u_alpha_a`

```{r eval = pars_eval[["u_alpha_a"]]}
histogram_and_ecdf_list("u_alpha_a")
```

## `u_alpha_as`

```{r eval = pars_eval[["u_alpha_as"]]}
histogram_and_ecdf_list("u_alpha_as")
```

## `u_alpha_xa`

```{r eval = pars_eval[["u_alpha_xa"]]}
histogram_and_ecdf_list("u_alpha_xa")
```

## `ui_lambda_x`

```{r eval = pars_eval[["ui_lambda_x"]]}
histogram_and_ecdf_list("ui_lambda_x")
```

## `ui_anc_rho_x`

```{r eval = pars_eval[["ui_anc_rho_x"]]}
histogram_and_ecdf_list("ui_anc_rho_x")
```

## `ui_anc_alpha_x`

```{r eval = pars_eval[["ui_anc_alpha_x"]]}
histogram_and_ecdf_list("ui_anc_alpha_x")
```

## `log_or_gamma`

```{r eval = pars_eval[["log_or_gamma"]]}
histogram_and_ecdf_list("log_or_gamma")
```

## `rho_t1_out`

There are too many variables to plot this here!

## `alpha_t1_out`

There are too many variables to plot this here!

## `lambda_t1_out`

There are too many variables to plot this here!

@@

### `beta`

```{r}
ks_plot_starts_with("beta")
```

### `logit`

```{r}
ks_plot_starts_with("logit")
```

### `log_sigma`

```{r}
ks_plot_starts_with("log_sigma")
```

### `u_rho_x`

```{r eval = pars_eval[["u_rho_x"]]}
ks_plot_starts_with("u_rho_x")
```

### `u_rho_xs`

```{r eval = pars_eval[["u_rho_xs"]]}
ks_plot_starts_with("u_rho_xs")
```

### `us_rho_x`

```{r eval = pars_eval[["us_rho_x"]]}
ks_plot_starts_with("us_rho_x")
```

### `us_rho_xs`

```{r eval = pars_eval[["us_rho_xs"]]}
ks_plot_starts_with("us_rho_xs")
```

### `u_rho_a`

```{r eval = pars_eval[["u_rho_a"]]}
ks_plot_starts_with("u_rho_a")
```

### `u_rho_as`

```{r eval = pars_eval[["u_rho_as"]]}
ks_plot_starts_with("u_rho_as")
```

### `u_alpha_x`

```{r eval = pars_eval[["u_alpha_x"]]}
ks_plot_starts_with("u_alpha_x")
```

### `u_alpha_xs`

```{r eval = pars_eval[["u_alpha_xs"]]}
ks_plot_starts_with("u_alpha_xs")
```

### `us_alpha_x`

```{r eval = pars_eval[["us_alpha_x"]]}
ks_plot_starts_with("us_alpha_x")
```

### `us_alpha_xs`

```{r eval = pars_eval[["us_alpha_xs"]]}
ks_plot_starts_with("us_alpha_xs")
```

### `u_alpha_a`

```{r eval = pars_eval[["u_alpha_a"]]}
ks_plot_starts_with("u_alpha_a")
```

### `u_alpha_as`

```{r eval = pars_eval[["u_alpha_as"]]}
ks_plot_starts_with("u_alpha_as")
```

### `u_alpha_xa`

```{r eval = pars_eval[["u_alpha_xa"]]}
ks_plot_starts_with("u_alpha_xa")
```

### `ui_anc_rho_x`

```{r eval = pars_eval[["ui_anc_rho_x"]]}
ks_plot_starts_with("ui_anc_rho_x")
```

### `ui_anc_alpha_x`

```{r eval = pars_eval[["ui_anc_alpha_x"]]}
ks_plot_starts_with("ui_anc_alpha_x")
```

### `log_or_gamma`

```{r eval = pars_eval[["log_or_gamma"]]}
ks_plot_starts_with("log_or_gamma")
```

### `rho_t1_out`

```{r}
ks_df_out(par = "rho_t1_out") %>%
  ks_plot(par = "rho_t1_out", alpha = 0.2)
```

### `alpha_t1_out`

```{r}
ks_df_out(par = "alpha_t1_out") %>%
  ks_plot(par = "rho_t1_out", alpha = 0.2)
```

### `lambda_t1_out`

```{r}
ks_df_out(par = "lambda_t1_out") %>%
  filter(!age_group %in% c("Y005_009", "Y010_014", "Y080_999")) %>%
  ks_plot(par = "lambda_t1_out", alpha = 0.2)
```

@@

ks_summary_latent <- filter(ks_summary, type == "Latent field")

@@

ks_summary_latent %>%
  ggplot(aes(x = TMB, y = aghq, col = parname, size = size)) +
  geom_point(alpha = 0.4) +
  xlim(0, xy_length) +
  ylim(0, xy_length) +
  scale_color_manual(values = extended_cbpalette(n = 20)) +
  scale_size_continuous(breaks = c(2, 10, 32), labels = c(2, 10, 32)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(x = "KS(TMB, NUTS)", y = "KS(PCA-AGHQ, NUTS)", col = "Parameter", size = "Length", subtitle = "Smaller KS values indicate higher accuracy") +
  theme_minimal() +
  guides(size = guide_legend(title.position = "top", direction = "vertical"), col = guide_legend(title.position = "top")) +
  theme(legend.position = "bottom", legend.title = element_text(size = rel(0.9)), legend.text = element_text(size = rel(0.7)))

@@

ks_df %>%
  filter(type != "Hyper") %>%
  mutate(method = fct_reorg(method, "TMB" = "TMB", "PCA-AGHQ" = "aghq")) %>%
  left_join(data.frame(ess) %>%
    tibble::rownames_to_column("par"),
  ) %>%
  ggplot(aes(x = ess, y = ks)) +
    geom_point(shape = 1, alpha = 0.5) +
    geom_smooth(method = "lm", color = "#56B4E9", fullrange = TRUE) +
    stat_poly_eq(use_label("eq"), label.x.npc = "right") +
    stat_poly_eq(label.y = 0.9, label.x.npc = "right") +
    scale_x_continuous(limits = c(0, NA)) +
    facet_grid(~ method) +
    theme_minimal() +
    labs(x = "ESS", y = "KS(method, NUTS)")

>>>>

<!-- ## `beta_rho` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf_list("beta_rho") -->
<!-- ``` -->

<!-- ## `beta_alpha` -->

<!-- ```{r eval = pars_eval[["beta_alpha"]]} -->
<!-- histogram_and_ecdf_list("beta_alpha") -->
<!-- ``` -->

<!-- ## `beta_lambda` -->

<!-- ```{r eval = pars_eval[["beta_lambda"]]} -->
<!-- histogram_and_ecdf_list("beta_lambda") -->
<!-- ``` -->

<!-- ## `beta_anc_rho` -->

<!-- ```{r eval = pars_eval[["beta_anc_rho"]]} -->
<!-- histogram_and_ecdf_list("beta_anc_rho") -->
<!-- ``` -->

<!-- ## `beta_anc_alpha` -->

<!-- ```{r eval = pars_eval[["beta_anc_alpha"]]} -->
<!-- histogram_and_ecdf("beta_anc_alpha") -->
<!-- ``` -->

<!-- ## `logit` -->

<!-- ```{r eval = FALSE} -->
<!-- lapply(pars[stringr::str_starts(pars, "logit")], histogram_and_ecdf) -->
<!-- ``` -->

<!-- ## `log_sigma` -->

<!-- ```{r eval = FALSE} -->
<!-- lapply(pars[stringr::str_starts(pars, "log_sigma")], histogram_and_ecdf) -->
<!-- ``` -->

<!-- ## `u_rho_x` -->

<!-- ```{r eval = pars_eval[["u_rho_x"]]} -->
<!-- histogram_and_ecdf_list("u_rho_x") -->
<!-- ``` -->

<!-- ## `us_rho_x` -->

<!-- ```{r eval = pars_eval[["us_rho_x"]]} -->
<!-- histogram_and_ecdf_list("us_rho_x") -->
<!-- ``` -->

<!-- ## `u_rho_xs` -->

<!-- ```{r eval = pars_eval[["u_rho_xs"]]} -->
<!-- histogram_and_ecdf_list("u_rho_xs") -->
<!-- ``` -->

<!-- ## `us_rho_xs` -->

<!-- ```{r eval = pars_eval[["us_rho_xs"]]} -->
<!-- histogram_and_ecdf_list("us_rho_xs") -->
<!-- ``` -->

<!-- ## `u_rho_as` -->

<!-- ```{r eval = pars_eval[["u_rho_as"]]} -->
<!-- histogram_and_ecdf_list("u_rho_as") -->
<!-- ``` -->

<!-- ## `u_alpha_x` -->

<!-- ```{r eval = pars_eval[["u_alpha_x"]]} -->
<!-- histogram_and_ecdf_list("u_alpha_x") -->
<!-- ``` -->

<!-- ## `us_alpha_x` -->

<!-- ```{r eval = pars_eval[["us_alpha_x"]]} -->
<!-- histogram_and_ecdf_list("us_alpha_x") -->
<!-- ``` -->

<!-- ## `u_alpha_xs` -->

<!-- ```{r eval = pars_eval[["u_alpha_xs"]]} -->
<!-- histogram_and_ecdf_list("u_alpha_xs") -->
<!-- ``` -->

<!-- ## `us_alpha_xs` -->

<!-- ```{r eval = pars_eval[["beta_rho"]]} -->
<!-- histogram_and_ecdf_list("us_alpha_xs") -->
<!-- ``` -->

<!-- ## `u_alpha_a` -->

<!-- ```{r eval = pars_eval[["u_alpha_a"]]} -->
<!-- histogram_and_ecdf_list("u_alpha_a") -->
<!-- ``` -->

<!-- ## `u_alpha_as` -->

<!-- ```{r eval = pars_eval[["u_alpha_as"]]} -->
<!-- histogram_and_ecdf_list("u_alpha_as") -->
<!-- ``` -->

<!-- ## `u_alpha_xa` -->

<!-- ```{r eval = pars_eval[["u_alpha_xa"]]} -->
<!-- histogram_and_ecdf_list("u_alpha_xa") -->
<!-- ``` -->

<!-- ## `ui_lambda_x` -->

<!-- ```{r eval = pars_eval[["ui_lambda_x"]]} -->
<!-- histogram_and_ecdf_list("ui_lambda_x") -->
<!-- ``` -->

<!-- ## `ui_anc_rho_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_rho_x"]]} -->
<!-- histogram_and_ecdf_list("ui_anc_rho_x") -->
<!-- ``` -->

<!-- ## `ui_anc_alpha_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_alpha_x"]]} -->
<!-- histogram_and_ecdf_list("ui_anc_alpha_x") -->
<!-- ``` -->

<!-- ## `log_or_gamma` -->

<!-- ```{r eval = pars_eval[["log_or_gamma"]]} -->
<!-- histogram_and_ecdf_list("log_or_gamma") -->
<!-- ``` -->

<!-- ## `rho_t1_out` -->

<!-- There are too many variables to plot this here! -->

<!-- ## `alpha_t1_out` -->

<!-- There are too many variables to plot this here! -->

<!-- ## `lambda_t1_out` -->

<!-- There are too many variables to plot this here! -->

@@

<!-- ### `beta` -->

<!-- ```{r} -->
<!-- ks_plot_starts_with("beta") -->
<!-- ``` -->

<!-- ### `logit` -->

<!-- ```{r} -->
<!-- ks_plot_starts_with("logit") -->
<!-- ``` -->

<!-- ### `log_sigma` -->

<!-- ```{r} -->
<!-- ks_plot_starts_with("log_sigma") -->
<!-- ``` -->

<!-- ### `u_rho_x` -->

<!-- ```{r eval = pars_eval[["u_rho_x"]]} -->
<!-- ks_plot_starts_with("u_rho_x") -->
<!-- ``` -->

<!-- ### `u_rho_xs` -->

<!-- ```{r eval = pars_eval[["u_rho_xs"]]} -->
<!-- ks_plot_starts_with("u_rho_xs") -->
<!-- ``` -->

<!-- ### `us_rho_x` -->

<!-- ```{r eval = pars_eval[["us_rho_x"]]} -->
<!-- ks_plot_starts_with("us_rho_x") -->
<!-- ``` -->

<!-- ### `us_rho_xs` -->

<!-- ```{r eval = pars_eval[["us_rho_xs"]]} -->
<!-- ks_plot_starts_with("us_rho_xs") -->
<!-- ``` -->

<!-- ### `u_rho_a` -->

<!-- ```{r eval = pars_eval[["u_rho_a"]]} -->
<!-- ks_plot_starts_with("u_rho_a") -->
<!-- ``` -->

<!-- ### `u_rho_as` -->

<!-- ```{r eval = pars_eval[["u_rho_as"]]} -->
<!-- ks_plot_starts_with("u_rho_as") -->
<!-- ``` -->

<!-- ### `u_alpha_x` -->

<!-- ```{r eval = pars_eval[["u_alpha_x"]]} -->
<!-- ks_plot_starts_with("u_alpha_x") -->
<!-- ``` -->

<!-- ### `u_alpha_xs` -->

<!-- ```{r eval = pars_eval[["u_alpha_xs"]]} -->
<!-- ks_plot_starts_with("u_alpha_xs") -->
<!-- ``` -->

<!-- ### `us_alpha_x` -->

<!-- ```{r eval = pars_eval[["us_alpha_x"]]} -->
<!-- ks_plot_starts_with("us_alpha_x") -->
<!-- ``` -->

<!-- ### `us_alpha_xs` -->

<!-- ```{r eval = pars_eval[["us_alpha_xs"]]} -->
<!-- ks_plot_starts_with("us_alpha_xs") -->
<!-- ``` -->

<!-- ### `u_alpha_a` -->

<!-- ```{r eval = pars_eval[["u_alpha_a"]]} -->
<!-- ks_plot_starts_with("u_alpha_a") -->
<!-- ``` -->

<!-- ### `u_alpha_as` -->

<!-- ```{r eval = pars_eval[["u_alpha_as"]]} -->
<!-- ks_plot_starts_with("u_alpha_as") -->
<!-- ``` -->

<!-- ### `u_alpha_xa` -->

<!-- ```{r eval = pars_eval[["u_alpha_xa"]]} -->
<!-- ks_plot_starts_with("u_alpha_xa") -->
<!-- ``` -->

<!-- ### `ui_anc_rho_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_rho_x"]]} -->
<!-- ks_plot_starts_with("ui_anc_rho_x") -->
<!-- ``` -->

<!-- ### `ui_anc_alpha_x` -->

<!-- ```{r eval = pars_eval[["ui_anc_alpha_x"]]} -->
<!-- ks_plot_starts_with("ui_anc_alpha_x") -->
<!-- ``` -->

<!-- ### `log_or_gamma` -->

<!-- ```{r eval = pars_eval[["log_or_gamma"]]} -->
<!-- ks_plot_starts_with("log_or_gamma") -->
<!-- ``` -->

<!-- ### `rho_t1_out` -->

<!-- ```{r} -->
<!-- ks_df_out(par = "rho_t1_out") %>% -->
<!--   ks_plot(par = "rho_t1_out", alpha = 0.2) -->
<!-- ``` -->

<!-- ### `alpha_t1_out` -->

<!-- ```{r} -->
<!-- ks_df_out(par = "alpha_t1_out") %>% -->
<!--   ks_plot(par = "rho_t1_out", alpha = 0.2) -->
<!-- ``` -->

<!-- ### `lambda_t1_out` -->

<!-- ```{r} -->
<!-- ks_df_out(par = "lambda_t1_out") %>% -->
<!--   filter(!age_group %in% c("Y005_009", "Y010_014", "Y080_999")) %>% -->
<!--   ks_plot(par = "lambda_t1_out", alpha = 0.2) -->
<!-- ``` -->

@@

ks_summary_latent <- filter(ks_summary, type == "Latent")

@@

ks_summary_latent %>%
  ggplot(aes(x = TMB, y = aghq - TMB, col = parname, size = size)) +
  geom_point(alpha = 0.7) +
  scale_color_manual(values = extended_cbpalette(n = 20)) +
  scale_size_continuous(breaks = c(2, 10, 32), labels = c(2, 10, 32)) +
  geom_abline(slope = 0, intercept = 0, linetype = "dashed") +
  labs(x = "KS(GEB, NUTS)", y = "KS(GPCA-AGHQ, NUTS) - KS(GEB, NUTS)", col = "Parameter", size = "Length") +
  theme_minimal() +
  guides(size = guide_legend(title.position = "top", direction = "vertical"), col = guide_legend(title.position = "top")) +
  theme(legend.position = "bottom", legend.title = element_text(size = rel(0.9)), legend.text = element_text(size = rel(0.65)))

@@

ks_df %>%
  filter(type != "Hyper") %>%
  mutate(method = fct_reorg(method, "GEB" = "TMB", "GPCA-AGHQ" = "aghq")) %>%
  left_join(data.frame(ess) %>%
    tibble::rownames_to_column("par"),
  ) %>%
  ggplot(aes(x = ess, y = ks)) +
    geom_point(shape = 1, alpha = 0.5) +
    geom_smooth(method = "lm", color = "#CC79A7", fullrange = TRUE) +
    ggpmisc::stat_poly_eq(ggpmisc::use_label("eq"), label.x.npc = "right") +
    ggpmisc::stat_poly_eq(label.y = 0.9, label.x.npc = "right") +
    scale_x_continuous(limits = c(0, NA)) +
    facet_grid(~ method) +
    theme_minimal() +
    labs(x = "NUTS ESS", y = "KS(approach, NUTS)")
